Pteropod exposure analysis

### 2018-03-15 expose.Rmd
comps by treatment for exposure

toplo2 <- expdat %>% 
  left_join(envdat, by = 'CTD') %>% 
  unite(`temp, pCO2`, temp_trt, pco2_trt, sep = '/') %>% 
  mutate(
    `temp, pCO2` = factor(`temp, pCO2`, levels = c('lo/lo', 'lo/hi', 'hi/lo' ,'hi/hi'))
  )

toplo3 <- toplo2 %>% 
  gather('var', 'val', -CTD, -`temp, pCO2`) %>% 
  group_by(CTD, var) %>% 
  summarize(
    val = mean(val, na.rm = T)
    ) %>% 
  spread(var, val)

selectInput("vr", "Choose a variable to plot again survivorship:", envchr)

  names(toplo2)[names(toplo2) %in% input$vr] <- 'xval'

  p <- ggplot(toplo2, aes(x = xval, y = alive)) + 
    geom_point(size = 5, aes(colour = `temp, pCO2`)) + 
    scale_y_continuous('% alive') + 
    theme_bw(base_family = 'serif') + 
    scale_x_continuous(input$vr) + 
    stat_smooth(method = 'lm') +
    ggtitle('all observations')

@@

ploav <- reactive({

  names(toplo3)[names(toplo3) %in% input$vr] <- 'xval'

  p <- ggplot(toplo3, aes(x = xval, y = alive)) + 
    geom_point(size = 5) + 
    scale_y_continuous('% alive') + 
    theme_bw(base_family = 'serif') + 
    scale_x_continuous(input$vr) + 
    stat_smooth(method = 'lm') + 
    ggtitle('Averaged by site')

@@

renderPlot({plovr()}, height = 300, width = 600)
renderPlot({ploav()}, height = 300, width = 600)
```

```{r}
# all correlations
crs <- crossing(var1 = 'alive', var2 = envchr) %>% 
  rownames_to_column() %>% 
  group_by(rowname) %>% 
  nest %>% 
  mutate(

@@

      # variables
      vr1 <- toplo3[[x$var1]]
      vr2 <- toplo3[[x$var2]]

@@

    })
  ) %>% 
  unnest %>% 
  select(-rowname) %>% 
  gather('cortyp', 'corval', pr, sp) %>% 
  spread(var2, corval)
```

```{r}
knitr::kable(crs, caption = 'Pearson and Spearman correlations, based on averages by site')
```

>>>>

toplo2 <- expdat %>% 
  left_join(envdat, by = 'CTD') %>% 
  unite(`temp, pCO2`, temp_trt, pco2_trt, sep = '/') %>% 
  mutate(
    `temp, pCO2` = factor(`temp, pCO2`, levels = c('lo/lo', 'lo/hi', 'hi/lo' ,'hi/hi')),
    alive_tr = asin(alive / 100)
  )

selectInput("vr", "Choose a variable to plot again survivorship:", envchr)
selectInput("trt", "Choose a treatment (temp, pCO2):", as.character(levels(toplo2$`temp, pCO2`)))

plovrid <- reactive({

  # assign variable selection to name
  names(toplo2)[names(toplo2) %in% input$vr] <- 'xval'

  # filter by treatment
  filt_toplo2 <- toplo2 %>% 
    filter(`temp, pCO2` %in% input$trt)

  p <- ggplot(filt_toplo2, aes(x = xval, y = alive)) + 
    geom_point(size = 5) + 
    scale_y_continuous('% alive') + 
    coord_cartesian(ylim = c(0, 105)) +
    theme_bw(base_family = 'serif') + 
    scale_x_continuous(input$vr) + 
    stat_smooth(method = 'lm') +
    ggtitle('identity')

@@

  # assign variable selection to name
  names(toplo2)[names(toplo2) %in% input$vr] <- 'xval'

  # filter by treatment
  filt_toplo2 <- toplo2 %>% 
    filter(`temp, pCO2` %in% input$trt)

  p <- ggplot(filt_toplo2, aes(x = xval, y = alive_tr)) + 
    geom_point(size = 5) + 
    scale_y_continuous('% alive (arcsine)') + 
    coord_cartesian(ylim = c(0, 1.4)) +
    theme_bw(base_family = 'serif') + 
    scale_x_continuous(input$vr) + 
    stat_smooth(method = 'lm') +
    ggtitle('transformed')

@@

renderPlot({plovrid()}, height = 300, width = 600)
renderPlot({plovr()}, height = 300, width = 600)
```

```{r, eval = T}
# all correlations
crs <- toplo2 %>% 
  select(-CTD) %>% 
  filter(!`temp, pCO2` %in% 'hi/hi') %>% 
  gather('var', 'val', -`temp, pCO2`, -alive_tr, -alive) %>% 
  gather('alvvr', 'alvvl', alive_tr, alive) %>% 
  group_by(`temp, pCO2`, alvvr, var) %>% 
  nest %>% 
  mutate(

@@

      # variables
      vr1 <- x$alvvl
      vr2 <- x$val

@@

    })
  ) %>% 
  select(-data) %>% 
  unnest %>% 
  gather('cortyp', 'corval', pr, sp) %>% 
  spread(var, corval) %>% 
  rename(response = alvvr) %>% 
  mutate(response = factor(response, levels = c('alive', 'alive_tr'), labels = c('identity', 'arcsine'))) %>% 
  arrange(cortyp, response, `temp, pCO2`)
```

```{r, eval = T}
knitr::kable(crs, caption = 'Pearson and Spearman correlations of survival (identity and arcsine) by variable')
```
